---
title: "HeadsUp RCT Analysis"
author: "Michelle K Jamieson"
date: "2022-09-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) # for data manipulation and visualization
library(here) # for easier file paths
library(skimr) # for summarizing data
library(gtsummary) # for creating tables
library(DataExplorer) # for automated data exploration
library(ggpubr) # for enhanced ggplot objects
library(patchwork) # for arranging ggplots
library(kableExtra) # for enhancing knitr tables
library(rstatix) # for easy statistical tests
```

# Introduction
Provide a brief introduction to the HeadsUp RCT, its objectives, and the significance of the analysis.

# Load Packages
Load all required packages upfront for ease of readability and organization. Packages are loaded in the setup chunk to keep the document clean and organized.

# Read in Data
Load the dataset using appropriate methods, ensuring confidentiality and data integrity.

```{r}
# Assuming the data file is in the same directory as the Rmd file.
file_path <- here("HeadsUpStage3_DATA_All_Batches_T0_T1_T2_T3_Oct.xlsx")
headsup_data <- read_excel(file_path, password = "HuPs3@OctC1C2T0123")
```

# Data Exploration
Use skimr and DataExplorer to get an initial understanding of the dataset's structure and contents.

```{r}
skim(headsup_data)
plot_missing(headsup_data)
```

# Data Preprocessing
Clean and preprocess the data, handling categorical variables, missing values, and any transformations required.

```{r}
# Sample preprocessing for 'living_arrangements'
headsup_data <- headsup_data %>%
  mutate(
    living_arrangements = recode(living_arrangements, 
                                 "Alone" = "Alone",
                                 "Alone (supported living)" = "Alone",
                                 "Living in group accommodation" = "Alone",
                                 # Add more as needed
                                 ),
    # Add more variables as needed
  )
```

# Data Analysis
Perform descriptive statistics, hypothesis testing, and any model fitting as per the objectives of the RCT.

```{r}
# Example: Descriptive statistics for 'age' by 'group'
headsup_data %>%
  group_by(group) %>%
  summarise(
    mean_age = mean(age, na.rm = TRUE),
    sd_age = sd(age, na.rm = TRUE)
  )
```

# Data Visualization
Visualize the data to uncover patterns, trends, and insights.

```{r}
# Example: Age distribution by group
headsup_data %>%
  ggplot(aes(x = age, fill = group)) +
  geom_histogram(alpha = 0.6, position = "identity") +
  theme_minimal() +
  labs(title = "Age Distribution by Group", x = "Age", y = "Count")
```

# Discussion
Discuss the findings, their implications, and any recommendations or conclusions that can be drawn from the analysis.